Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments

### 2019-05-21 article.tex
Added template requirements

% Metadata Information
\acmConference{SAP}{September 2019}{Barcelona}
%\acmVolume{9}
%\acmNumber{4}
%\acmArticle{39}
%\acmYear{2010}
%\acmMonth{3}
%\acmArticleSeq{11}

%Copyright
\setcopyright{usgovmixed}

% DOI
\acmDOI{0000001.0000001}

@@

\title{Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments}

@@

\begin{abstract}
	Our aim is to build a portable active navigation system for the visually impaired that uses active perception techniques and a combination of feedback modes to identify a scene and guide a user to their destination.
	Such a system requires a non-visual feedback interface and in this paper we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
	The secondary goal is to determine how variations to the pitch rate of change affect the user's performance.
	For this, we conducted a set of experiments with blindfolded and user with visual impairments and found that, with some limitations, a spatialised audio tone with a varying pitch component can successfully convey a target's pan and tilt angles. 
\end{abstract} 
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003121.10011748</concept_id>
<concept_desc>Human-centered computing~Empirical studies in HCI</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003122.10003334</concept_id>
<concept_desc>Human-centered computing~User studies</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

>>>>

% Metadata Information
\acmConference[SAP '19]{Barcelona '19: ACM Symposium on Applied Perception}{September 2019}{Barcelona, Spain}
%\acmVolume{9}
%\acmNumber{4}
%\acmArticle{39}
%\acmYear{2010}
%\acmMonth{3}
%\acmArticleSeq{11}

%Copyright
\setcopyright{acmcopyright}
\copyrightyear{2019}

% DOI
\acmDOI{0000001.0000001}
\acmYear{2019}

@@

\title[Active Perception Interface for People with Visual Impairments]{Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments}

@@

\begin{CCSXML}
  <ccs2012>
    <concept>
      <concept_id>10003120.10003121.10011748</concept_id>
      <concept_desc>Human-centered computing~Empirical studies in HCI</concept_desc>
      <concept_significance>500</concept_significance>
    </concept>
    <concept>
      <concept_id>10003120.10003121.10003122.10003334</concept_id>
      <concept_desc>Human-centered computing~User studies</concept_desc>
      <concept_significance>300</concept_significance>
    </concept>
  </ccs2012>
\end{CCSXML}

@@

\begin{abstract}
	Our aim is to build a portable active navigation system for the visually impaired that uses active perception techniques and a combination of feedback modes to identify a scene and guide a user to their destination.
	Such a system requires a non-visual feedback interface and in this paper we investigate the effectiveness of a spatial audio tone with a varying pitch component, played through bone-conducting headphones, in conveying the pan and tilt angles of a target to the user in a pointing task.
	The secondary goal is to determine how variations to the pitch rate of change affect the user's performance.
	For this, we conducted a set of experiments with blindfolded and user with visual impairments and found that, with some limitations, a spatialised audio tone with a varying pitch component can successfully convey a target's pan and tilt angles. 
\end{abstract}
